Bayesian Sparsification of Deep $\cplx$-valued networks

### 2020-03-24 paper/paper.tex
thorough proofread X (appendix) * move section A after sectiion C * reverted back to onecolumn format

\documentclass[a4paper,10pt,twocolumn]{article}

@@

Each figure shows the compression-accuracy trade-off of a particular method and input features
for \textit{SimpleConvModel} and \textit{TwoLayerDenseModel} models for all four of the studied
datasets (described in the main text): \emph{top-left} EMNIST-Letters, \emph{top-right} KMNIST,
\emph{bottom-left} Fashion MNIST, and \emph{bottom-right} MNIST.
%
Figures \ref{fig:appendix__mnist-like__trade-off__ARD__fft}, \ref{fig:appendix__mnist-like__trade-off__VD__fft},
\ref{fig:appendix__mnist-like__trade-off__ARD__raw}, and \ref{fig:appendix__mnist-like__trade-off__VD__raw}
present $\real$ and $\cplx$ models with \emph{the same architecture}. We also report the
trade-off comparison, when the argument by \citet{monning_evaluation_2018} for higher intrinsic
capacity of $\cplx$-valued networks has been taken into account.
%
We compare $\real$ networks against $\tfrac12 \cplx$ with half the number of parameters
for raw input features on figures \ref{fig:appendix__cmp__mnist-like__trade-off__ARD__raw},
and \ref{fig:appendix__cmp__mnist-like__trade-off__VD__raw}, and $2 \real$ with
double the number of parameters against $\cplx$ for Fourier input features on figures
\ref{fig:appendix__cmp__mnist-like__trade-off__ARD__fft} and
\ref{fig:appendix__cmp__mnist-like__trade-off__VD__fft}.

>>>>

\documentclass[a4paper,10pt,onecolumn]{article}

@@

The plots presented in this appendix support the conclusions made in the main text and
provide an overview of the experiments conducted on MNIST-like datasets.

Each figure shows the compression-accuracy trade-off of a particular method and input
features for \textit{SimpleConvModel} and \textit{TwoLayerDenseModel} models for all four
of the studied datasets (described in the main text): EMNIST-Letters on the \textit{top-left},
KMNIST -- \textit{top-right}, Fashion MNIST -- \textit{bottom-left}, and MNIST on the
\textit{bottom-right}.
%
Figures \ref{fig:appendix__mnist-like__trade-off__ARD__fft}, \ref{fig:appendix__mnist-like__trade-off__VD__fft},
\ref{fig:appendix__mnist-like__trade-off__ARD__raw}, and \ref{fig:appendix__mnist-like__trade-off__VD__raw}
present $\real$ and $\cplx$ models with \textit{the same intermediate feature sizes}.

We also report the trade-off comparison, when the argument by \citet{monning_evaluation_2018}
for higher intrinsic capacity of $\cplx$-valued networks has been taken into account.
%
We compare $\real$ networks against $\tfrac12 \cplx$ with half the number of parameters
for raw input features on figures \ref{fig:appendix__cmp__mnist-like__trade-off__ARD__raw},
and \ref{fig:appendix__cmp__mnist-like__trade-off__VD__raw}, and $2 \real$ with
double the number of parameters against $\cplx$ for Fourier input features on figures
\ref{fig:appendix__cmp__mnist-like__trade-off__ARD__fft} and
\ref{fig:appendix__cmp__mnist-like__trade-off__VD__fft}.
